Domain-Driven, Generative Data Model for BigPetStore

### 2014-07-23 bdcloud_paper/latex/paper.tex
Added namedb description

where $Z$ is the normalization factor.  Given the small size ($\approx$30,000 zip codes) of the data set, $Z$ can be found directly by iterating over all of the zip codes and summing the scores. The population and household income data for the zip codes were taken from from the U.S. Census American Community Survey \cite{ACS}.  The stores' locations are generated by sampling zip codes from the PDF using a Roulette Wheel sampler.

@@

The probability of choosing zip code $z$ is given by

\begin{equation*}
p(\text{location} = \text{z}) = \frac{w_z}{\sum_{z} w(z)}
\end{equation*}

\textcolor{red}{names}

The customer locations are sampled from the PDF using a Roulette Wheel sampler.

@@

The probability $p(X=i)$ of choosing item category $i$ is given by

\begin{equation*}
p(X=i) = \frac{w_i}{\sum_i w_i}.
\end{equation*}

The item category for the purchase is chosen using a Roulette Wheel sampler.

>>>>

where $Z$ is the normalization factor.  Given the small size ($\approx$30,000 zip codes) of the data set, $Z$ can be found directly by iterating over all of the zip codes and summing the scores. The population and household income data for the zip codes were taken from from the U.S. Census American Community Survey \cite{ACS}.  The stores' locations are generated by sampling zip codes from the PDF.

@@

The customer's zip code is chosen by sampling from the zip codes with the probabiltiy of each zip code $z$ proportionate to its weight $w_z$.

Names are generated using data from the Name Database\cite{NameDB}. Each record in the database gives a name, a weight, and flag indicatings if the name can be used as a first name, a last name, or both.  PDFs generated for the first and last names using the weights.  The customer's name is generated by sampling a first name and a last name from each PDF respectively.

@@

The item category for each purchase is chosen by sampling from the item categories with the probability of each item category $i$ proportionate to its weight $w_i$.
